Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML

### 2014-02-24 paper.tex
Reworded in small ways to keep up an emphasis on this being a hypothetical design approach.

Whilst there are successful general web search engines such as Google that
will find any piece of content, there is a perceived need for a specific
search that makes better use of the internal knowledge the broadcasting
industry (e.g. BBC) has about its own content. The British Broadcasting
Corporation (BBC) is a public service broadcaster funded by the licence
fee paid by United Kingdom households. This industry-based case study
combines Soft Systems Methodology (SSM) and Unified Modelling Language
(UML) to design a high-level view of a search application that receives
web content from a variety of BBC content production systems and makes
every item then searchable by a BBC website visitor using the search
feature. The developers of such search applications can benefit from this
specific industry-based case study that contextualised the problem space
using SSM and developed UML models to solve the problem.

@@

@@

Dogan and Henshaw\cite{dogan2010transition}
showed how a ‘soft’ systems approach called Interactive
Management can be adopted to capture the requirements and contextualise the
problem space. This involved the process of transitioning from the soft systems
results to a formal model (e.g. UML). This transition was enabled by dividing
the actors in the rich pictures into meta-level and direct users of the system.
Although this division was subjective and depended on the interpretation  and
analysis of the rich pictures to provide a structure for the use case model,
the rich pictures themselves were created through interactions with subject
matter experts. The soft systems, and hence the Interactive Management results,
provided the baseline information to derive a formal model including UML use
case, sequence and domain models. The transitioning from ``soft'' to ``hard''
systems can be set within the State of the Art including the requirements
analysis and modelling as used in SSM, UML and Business Process Modelling.

@@

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model\cite{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around users seeking educational
and informative material such as \emph{Bitesize}
\footnote{\emph{Bitesize} is the name given to the BBC's free web-based
study materials for school children aged between
5 and 16, covering varying curricula for England, Wales and Scotland.}
or any other learning resources.

@@

These decisions relate to how the system would implement the data model
in Fig.~\ref{model}. The ontology described is an aggregation
of several efforts by Raimond\cite{raimond2009bbc}, Rayfield
\cite{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

@@

Thus even if the use case and domain models are not as comprehensive or
as honed as they need to be to build the entire application, they serve
their purpose adequately to communicate the first iterations of
development or -- especially in the case of the domain model -- information
pertaining to the whole organisation, even if only small parts of it are
they modelled directly in the application being built.

The sequence diagrams seemed to provoke more debate of the merits of
returning rich information in a single response versus an AJAX-driven
approach (or some trade-off in between). Again, the authors would emphasise the
communication aspect of UML modelling and argue that encouraging such debate
is a successful application of UML, not a failure because a decision
has not been made between two designs at this early stage.

@@

In conclusion, the UML modelling presented is a key part of solving
the BBC search problem, but it is far from sufficient in its own right.
Designing to the level of detail required would result in a rigid
development plan that made unverified assumptions, but an iterative
approach to modelling that starts at a high-level and updates as
development progresses could be used successfully in such a project.

>>>>

Whilst there are successful general web search engines such as Google that
will find any piece of content, there is a perceived need for a specific
search that makes better use of the internal knowledge the broadcasting
industry (e.g. BBC) has about its own content. The British Broadcasting
Corporation (BBC) is a public service broadcaster funded by the licence
fee paid by United Kingdom households. This industry-based case study
looks at the applicability of Soft Systems Methodology (SSM) and
Unified Modelling Language (UML) to design a hypothetical, high-level
view of a search application that receives
web content from a variety of BBC content production systems and makes
every item then searchable by a BBC website visitor using the search
feature. The developers of such search applications can benefit from this
specific industry-based case study that contextualised the problem space
using SSM and developed UML models to solve the problem.

@@

Whilst the BBC website currently has a
functional search feature already, this paper assumes building a new search application
from the ground up so as to give full freedom to apply the analysis and design
techniques therein. In practice, there are engineering challenges involved
in maintaining and building on top of existing systems. Such challenges
are out of scope for this paper.

@@

Dogan and Henshaw\cite{dogan2010transition}
showed how a ``soft'' systems approach called Interactive
Management can be adopted to capture the requirements and contextualise the
problem space. This involved the process of transitioning from the soft systems
results to a formal model (e.g. UML). This transition was enabled by dividing
the actors in the rich pictures into meta-level and direct users of the system.
Although this division was subjective and depended on the interpretation  and
analysis of the rich pictures to provide a structure for the use case model,
the rich pictures themselves were created through interactions with subject
matter experts. The soft systems, and hence the Interactive Management results,
provided the baseline information to derive a formal model including UML use
case, sequence and domain models. The transitioning from ``soft'' to ``hard''
systems can be set within the State of the Art including the requirements
analysis and modelling as used in SSM, UML and Business Process Modelling.

@@

It has been expressed already that a BBC-wide search application
would need to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model\cite{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collect all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around users seeking educational
and informative material such as \emph{Bitesize}
\footnote{\emph{Bitesize} is the name given to the BBC's free web-based
study materials for school children aged between
5 and 16, covering varying curricula for England, Wales and Scotland.}
or any other learning resources.

@@

These decisions relate to how the system would implement the data model
in Fig.~\ref{model}. The ontology described is an aggregation
of several efforts by Raimond\cite{raimond2009bbc}, Rayfield
\cite{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
of business models across different applications would only
harm maintainability.

@@

Thus even if the use case and domain models are not as comprehensive or
as honed as they need to be to build an entire application, they serve
their purpose adequately to communicate the first iterations of
development or -- especially in the case of the domain model -- information
pertaining to the whole organisation, even if only small parts of it are
they modelled directly in the application being built.

The sequence diagrams seem to provoke more debate of the merits of
returning rich information in a single response versus an AJAX-driven
approach (or some trade-off in between). Again, the authors would emphasise the
communication aspect of UML modelling and argue that encouraging such debate
is a successful application of UML, not a failure because a decision
has not been made between two designs at this early stage.

@@

In conclusion, the UML modelling presented communicates some promising
approaches to
the BBC search problem, but it is far from sufficient in its own right.
Designing to the level of detail required would result in a rigid
development plan that made unverified assumptions, but an iterative
approach to modelling that starts at a high-level and updates as
development progresses could be used successfully in such a project.
